Modeling Human Interactions in Collaborative Interactive Evolutionary Computation

### 2017-02-02 2017-GECCO-Modeling-User-Interactions-in-IEC/paper-body.tex
Complete Image
Interfaces

\begin{figure*}[!t]
    \centering
        \includegraphics[width=4.5in]{img/framework.eps}
    \caption{IEC Human-centered framework.}
    \label{fig:hc_framework}
\end{figure*}

@@

\subsection{Interfaces}
%They are Sensor and Web,

>>>>

\begin{figure*}[!t]
    \centering
        \includegraphics[width=5in]{img/framework.eps}
    \caption{IEC Human-centered framework.}
    \label{fig:hc_framework}
\end{figure*}

@@

\subsection{Interfaces}
The appropiate human interface will depend on the application domain, the current framework implemantation  
employs a web based application. Developers can use different templates, to present one or more phenotypes 
at a time, and the type of rating system: like or one to five stars. Another implementations do not need a
graphical interface at all, for example the EvoDraw instalation or the XYZ Project \cite{de2014artists}.
